---
author: "Aimer G. Diaz"
output: github_document
bibliography: References.bib
link-citations: true
csl: https://raw.githubusercontent.com/citation-style-language/styles/master/biomed-central.csl
---

# Alphafold2 monomer or oligomer prediction

<!-- Alphafold and RNA-binding domain scripts -->
# Viral proteins structure prediction

## Disorder domain prediction 

### Plaac 

[Plaac](plaac.wi.mit.edu) 

### From Alphafold pLDDT to disorder score 
[AlphaFold-disorder](https://github.com/BioComputingUP/AlphaFold-disorder )

<!-- for f in `grep ">" viralProteins.ol.fa `; do name=` echo $f | tr -d ">"` ; grep -A1  $name viralProteins.ol.fa > $name.fa; done

for f  in CaMV_P3/CaMV_P3/ranked_*.pdb  CaMV_P3_rnk0.pdb ; do awk -v i=1 '{sum+=$11; i=i+1 }END{print FILENAME,sum/i;}' $f ; done 

for f  in ` ls  [A-Z]*_*fa| egrep -v "CaMV_P6|CaMV_P4"`; do name=`basename -s ".fa" $f`; sbatch alfafold_monomer-disorder.sb $f $name ; wait 1800; done 

mv CaMV_P4/CaMV_P4/ranked_0.pdb CaMV_P4_rnk0.pdb

for f in `grep ">" viralProteins.ol.fa | egrep -wv "TYMV_206K|TRoV_P2a|TCV_P8|TCV_P88"`; do name=` echo $f | tr -d ">"` ; echo -ne "$name\t" ;   score=`grep -A 1  order $name/$name/ranking_debug.json  | grep -v order  | grep -oP "(model.*?)(?=\")" ` ; grep $score $name/$name/ranking_debug.json | head -n 1 ; done  | awk -F'\t|:|,' '{print $1"\t"$3}'

P88 has an X aa which disrtupt alphafold prediction,  the solution applied was to remove that single aa, which is enconded by a stop codon, separating Protein p28 protein from 	RNA-directed RNA polymerase, visualized on  https://web.expasy.org/translate/ , the X aa is a common representation for several viral proteins as shown here https://www.ncbi.nlm.nih.gov/Structure/cdd/cddsrv.cgi?uid=438090#seqalign 
-->
```{bash, eval=FALSE}
awk -v OFS="\t" 'NR==1 {print "AA","Chain","PAA","pLDDT"} !a[$4""$5""$6""$11]++ && $11 ~ /[0-9]/{print $4,$5,$6,$11}' P6_dimmer_model.pdb  CaMV_P6_rnk0.pdb  > CaMV_P6_plddt.txt 
```

```{r}
library(ggplot2, quietly = F) 
CaMV_P6 <- read.csv("CaMV_P6_plddt.txt", header = T, sep = "\t") 
CaMV_P6$Chain <- gsub(pattern = "A", replacement = "Monomer", CaMV_P6$Chain)
CaMV_P6$Chain <- gsub(pattern = "B", replacement = "Dimer-Left", CaMV_P6$Chain)
CaMV_P6$Chain <- gsub(pattern = "C", replacement = "Dimer-Right", CaMV_P6$Chain)
CaMV_P6_plot <- ggplot(CaMV_P6, aes(x=PAA, y=pLDDT, color=Chain)) + 
  geom_line() + geom_point() + ggtitle("pLDDT CaMV P6 as monomer and dimer") +
theme_classic() + theme(plot.title = element_text(hjust = 0.5))
CaMV_P6_plot
```

```{bash, eval=FALSE}
awk -v OFS="\t" 'NR==1 {print "AA","Chain","PAA","pLDDT"} !a[$4""$5""$6""$11]++ && $11 ~ /[0-9]/{print $4,"2a",$6,$11}' CMV_2a_rnk0.pdb > CMV2a_GRBP7dis.txt 
awk -v OFS="\t" '!a[$4""$5""$6""$11]++ && $11 ~ /[0-9]/{print $4,"G3BP7",$6,$11}' AtG3BP7_AF.pdb >> CMV2a_GRBP7dis.txt 
# Interaction polarity CMV 2a vs GRBP7
awk -v OFS="\t" '!a[$4""$5""$6""$11]++ && $11 ~ /[0-9]/{prot=$5;gsub("B","2a-right", prot);gsub("C","GRBP7-left", prot);print $4,prot,$6,$11}' CMV2a_GRBP7dis_model_3.cor.pdb >> CMV2a_GRBP7dis.txt
# Change of order GRBP7 vs CMV 2a 
awk -v OFS="\t" '!a[$4""$5""$6""$11]++ && $11 ~ /[0-9]/{prot=$5;gsub("C","2a-left", prot);gsub("B","GRBP7-right", prot);print $4,prot,$6,$11}' GRBP7dis_CMV2a_model_3.cor.pdb >> CMV2a_GRBP7dis.txt  
#cut -f 2 CMV2a_GRBP7dis.txt | sort | uniq -cd 
#%s/  / /g 
#%s/-/ /g
#%s/  / /g 
```  

```{r}
CMV2a_GRBP7 <- read.csv("CMV2a_GRBP7dis.txt", header = T, sep = "\t") 
GRBP7 <- CMV2a_GRBP7[!grepl("2a", CMV2a_GRBP7$Chain),]
CMV2a<- CMV2a_GRBP7[grepl("2a", CMV2a_GRBP7$Chain),]

CMV2a_plot <- ggplot(CMV2a, aes(x=PAA, y=pLDDT, color=Chain)) + 
  geom_line() + geom_point() + ggtitle("pLDDT CMV A6 as monomer and heterodimer") +
theme_classic() + theme(plot.title = element_text(hjust = 0.5))

GRBP7_plot <- ggplot(GRBP7, aes(x=PAA, y=pLDDT, color=Chain)) + 
  geom_line() + geom_point() + ggtitle("pLDDT GRBP7 as monomer and heterodimer") +
theme_classic() + theme(plot.title = element_text(hjust = 0.5))
GRBP7_plot
```
### MobiDB 
[MobiDB-lite](https://github.com/BioComputingUP/MobiDB-lite)
# sources
alphafold colors
https://github.com/busrasavas/pymol-color-alphafold
run https://raw.githubusercontent.com/cbalbin-bio/pymol-color-alphafold/master/coloraf.py
coloraf

https://www.rcsb.org/structure/5a9e

* move sequence
https://sourceforge.net/p/pymol/mailman/message/10098601/
Set the mouse in editing mode.  
Hold the shift key and put the mouse on  any atom of the ligand. 
While holding the shift key, press the mouse wheel 

* delete chain
https://www.researchgate.net/post/How_to_delete_complete_chain_of_protein_in_PyMol

* show sequence
https://pymolwiki.org/index.php/Seq_view
set seq_view, 1

[Composuitional bais, significant functional associations and protein disorder values](https://www.ncbi.nlm.nih.gov/pmc/articles/PMC1618407/) :
**N**	Gropu members 58 Mean disorder (D) value	0.45, functions in *Drosophila*	GO:0005634 [19]; nucleus (3 × 10-2)
		GO:0003729 [16]; mRNA binding (1 × 10-7)
		GO:0003723 [16]; RNA binding (1 × 10-11)
Videos to Gif 
https://convertio.co/download/4e3e62c5f5e6ba5448da7c243ea50079452818/ 
Filling models 
[AlphaFill](https://www.nature.com/articles/s41592-022-01685-y)

Rosetta predictions, for 3a CMV movement protein
https://www.ebi.ac.uk/interpro/entry/InterPro/IPR000603/rosettafold/

2b or Suppressor of silencing 2b dimer and tetramer soon to be published 
https://www.rcsb.org/structure/3cz3

# Structure conservation and sequence evolution 

[Evidence of a novel viral membrane fusion mechanism shared by the Hepaci, Pegi and Pestiviruses](https://www.biorxiv.org/content/10.1101/2022.10.18.512720v1) , [protein models](https://zenodo.org/record/7221315#.Y4869b7MIUE) 